25 years of Social Work Research

### 2015-02-26 dataCleaning.Rmd
Code clean up.
Identifies and eliminates ineligible records.

load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/PsycInfo.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")

@@

@@

  #Combines EbscoHost and ProQuest Wrangles, and strips out article attributes 
  #from duplicate entries
  combined.DF<-rbind(ebscoBWR.df, proQuestBWR.df)
  full.df<-combined.DF[!(combined.DF$articleID %in% jointTitles.dup.ID), ]

>>>>

load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/PsycInfo.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)

load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")
hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)
```

@@

#Identify records that were incorrectly captured in the wrangle
#using regular expressions
insert.1<-"[B|b]ook [R|r]eview.|^[F|f]orum|[F|f]orum$|[C|c]ommentary|Comments on"
insert.2<-"^[I|i]ndex [T|t]o|[I|i]ntroduction:|[I|i]ntroduction [T|t]o|\\([B|b]ook\\)"
insert.3<-"[H|h]andbook|Volume|volumes|newsletters|[L|l]etter from"
insert.4<-"[P|p]reface|\\([0-9]{4}-[0-9]{4}\\):|: [A|a] [R|r]esponse [T|t]o [B-Z]"
insert.5<-"[S|s]pecial [I|i]ssue|[T|t]able [O|o]f [C|c]ontent|\\([U|u]ndetermined"
insert<-paste(insert.1,insert.2,insert.3,insert.4,insert.5, sep="|")

badRecords<-subset(jointTitles, grepl(insert, record))
badRecords.ID<-badRecords$articleID

@@

  #Combines EbscoHost and ProQuest Wrangles, and 
  combined.DF<-rbind(ebscoBWR.df, proQuestBWR.df)

  #Strips out article attributes from inelligble records
  combined.DF<-combined.DF[!(combined.DF$articleID %in% badRecords.ID), ]

  #strips out article attributes from duplicate records
  full.df<-combined.DF[!(combined.DF$articleID %in% jointTitles.dup.ID), ]
